Papers

### 2025-02-11 quarto/index.qmd
update

**Aston Zhang** is a research scientist on the <a href="https://llama.meta.com/" target="_blank">Llama</a> team at Meta Generative AI and a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
Previously, he served as a scientist and manager at AWS AI Research.
His accolades include the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
the ACM Ubicomp Distinguished Paper Award,
and an ACM SenSys Best Paper Award nomination.
His textbook, "<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>," 
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He holds a Ph.D. in Computer Science from the University of Illinois Urbana-Champaign.

>>>>

**Aston Zhang** is a research scientist on the <a href="https://llama.meta.com/" target="_blank">Llama</a> team at Meta Generative AI, where he leads long context of Llama 4 and is a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
Previously, he served as a scientist and manager at AWS AI Research.
His accolades include the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
the ACM Ubicomp Distinguished Paper Award,
and an ACM SenSys Best Paper Award nomination.
His textbook, "<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>," 
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He holds a Ph.D. in Computer Science from the University of Illinois Urbana-Champaign.
